% =====================================================================
% Curriculum Vitae - Xiangyu Chen
% Compile with: pdflatex Xiangyu_Chen_CV.tex
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.7cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\definecolor{linkblue}{RGB}{0,82,155}
\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue}

% --- Section style: small-caps bold heading with a full-width rule ----
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\vspace{-0.5em}\rule{\textwidth}{0.8pt}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\setlist[itemize]{leftmargin=1.4em, itemsep=1pt, topsep=2pt, parsep=0pt}
\setlist[enumerate]{leftmargin=2.1em, itemsep=2pt, topsep=2pt, parsep=0pt}

\setlength{\parindent}{0pt}
\newcommand{\dateit}[2]{\textbf{#1}\hfill #2\par}

\begin{document}
\pagestyle{empty}

% ----------------------------- Header --------------------------------
\begin{center}
  {\Huge\bfseries Xiangyu Chen}\\[5pt]
  {\small Ph.D. Student, MARS Lab, School of MAE, Nanyang Technological University, Singapore}\\[4pt]
  {\small
    \href{mailto:cxy980212@gmail.com}{cxy980212@gmail.com}
    \quad\textbar\quad +86\,152\,5415\,6088
    \quad\textbar\quad \href{https://xyc0212.github.io}{xyc0212.github.io}
    \quad\textbar\quad \href{https://scholar.google.com/citations?user=wEV8pmkAAAAJ}{Google Scholar}
    \quad\textbar\quad \href{https://github.com/XyC0212}{GitHub}
  }
\end{center}

% ---------------------------- Education ------------------------------
\section{Education}
\dateit{Nanyang Technological University, Singapore}{2025 -- Present}
Ph.D. in Mechanical and Aerospace Engineering (MARS Lab). Advisor: Prof.\ Jianfei Yang.

\smallskip
\dateit{Shandong University, Jinan, China}{Sep 2020 -- Jun 2023}
M.Eng.\ in Control Science and Engineering. GPA: 89.4/100 (Rank 1/116). National Scholarship (top 1\%).

\smallskip
\dateit{University of Jinan, Jinan, China}{Sep 2016 -- Jun 2020}
B.Eng.\ in Electrical Engineering and Automation. GPA: 89.7/100 (Rank 4/403). National Scholarship (top 1\%), Government Scholarship (top 1\%), Song Jian Scholarship (top 0.1\%).

\smallskip
\textbf{Standardized Tests:} TOEFL 106 (R29 / L27 / S23 / W27); GRE 319 + 3.5.

% ------------------------ Research Interests -------------------------
\section{Research Interests}
Robotic manipulation, dexterous manipulation, embodied AI, and imitation/reinforcement learning for robot policy learning.

% ---------------------------- Publications ---------------------------
\section{Publications}
{\small \textbf{Bold} denotes the author. ($^{\dagger}$ co-first author where applicable.)}
\begin{enumerate}[label={[\arabic*]}]
  \item \textbf{X.\ Chen}, Y.\ Hu, C.\ Zhou, J.\ Yang. ``Rethinking Implicit Spatial Representation in Visuomotor Policy Learning.'' \textit{arXiv:2606.15232}, 2026.
  \item J.\ Li, Y.\ Hu, H.\ Geng, \textbf{X.\ Chen}, C.\ Zhou, Z.\ Cui, J.\ Yang. ``M\textsuperscript{3}A Policy: Mutable Material Manipulation Augmentation Policy through Photometric Re-rendering.'' \textit{IEEE/CVF CVPR (Findings)}, 2026.
  \item J.\ Jia, T.\ An, Y.\ Hu, G.\ Li, J.\ Li, B.\ Hou, \textbf{X.\ Chen}, J.\ Bai, B.\ Lyu, J.\ Yang. ``MARS Policy: Multimodality Only When It Matters.'' \textit{arXiv:2605.29766}, 2026.
  \item J.\ Bai, J.\ Jia, Y.\ Hu, G.\ Li, \textbf{X.\ Chen}, T.\ An, K.\ Zuo, J.\ Yang. ``FLASH: Efficient Visuomotor Policy via Sparse Sampling.'' \textit{arXiv:2605.15492}, 2026.
  \item J.\ Jia, G.\ Li, \textbf{X.\ Chen}, T.\ An, Y.\ Hu, J.\ Li, X.\ Guo, J.\ Yang. ``A2A: Action-to-Action Flow Matching for Robot Policy Learning.'' \textit{Robotics: Science and Systems (RSS)}, 2026.
  \item \textbf{X.\ Chen}, C.\ Zhou, Y.\ Liu, J.\ Yang. ``RM-RL: Role-Model Reinforcement Learning for Precise Robot Manipulation.'' \textit{IEEE Int.\ Conf.\ on Robotics and Automation (ICRA)}, 2026.
  \item \textbf{X.\ Chen}, F.\ Yang, C.\ Wang. ``iA*: Imperative Learning-based A* Search for Pathfinding.'' \textit{IEEE Robotics and Automation Letters (RA-L)}, 2025.
  \item C.\ Wang, \textbf{X.\ Chen}, C.\ Li, R.\ Song, Y.\ Li, M.\ Q.-H.\ Meng. ``Chase and Track: Toward Safe and Smooth Trajectory Planning for Robotic Navigation in Dynamic Environments.'' \textit{IEEE Trans.\ on Industrial Electronics}, 70(1):604--613, 2022.
  \item \textbf{X.\ Chen}, J.\ Liu, J.\ Wu, C.\ Wang, R.\ Song. ``LoPF: An Online LiDAR-Only Person-Following Framework.'' \textit{IEEE Trans.\ on Instrumentation and Measurement}, 71:1--13, 2022.
  \item \textbf{X.\ Chen}, Y.\ Wang, C.\ Wang, R.\ Song, Y.\ Li. ``Low-drift LiDAR-only Odometry and Mapping for UGVs in Environments with Non-level Roads.'' \textit{IEEE/RSJ IROS}, pp.\ 13174--13180, 2022.
  \item Y.\ Wang, M.\ Xu, \textbf{X.\ Chen}, X.\ Zhang, C.\ Wang, R.\ Song. ``Information Map Prediction based on Learning Network for Reinforced Autonomous Exploration.'' \textit{IEEE ROBIO}, pp.\ 1982--1988, 2022.
\end{enumerate}

% ----------------------------- Experience ----------------------------
\section{Experience}
\dateit{Graduate Research --- MARS Lab, Nanyang Technological University}{2025 -- Present}
\begin{itemize}
  \item Embodied AI agents for life science: robotic and dexterous manipulation, and visuomotor policy learning that pairs foundation models with robotic arms for Chem/Bio lab automation.
\end{itemize}

\dateit{Research Intern --- MegaRobo, Beijing, China}{Nov 2024 -- Jan 2025}
\dateit{Research Intern --- Realman, Beijing, China}{May 2024 -- Aug 2024}

\dateit{Research Intern (Remote) --- SAIR Lab}{Sep 2023 -- Sep 2024}
\begin{itemize}
  \item Imperative-learning-based A* pathfinding; contributed Spline and ICP modules to the open-source PyPose library.
\end{itemize}

\dateit{Graduate Research --- Shandong University}{2020 -- 2023}
\begin{itemize}
  \item LiDAR SLAM and localization on non-level roads, safe and smooth trajectory planning, and LiDAR-only person-following for mobile and quadruped robots.
\end{itemize}

\dateit{Research Intern --- Yobotics, Jinan, China}{May 2020 -- Jul 2020}

% --------------------------- Honors & Awards -------------------------
\section{Honors \& Awards}
\begin{itemize}
  \item National Scholarship for Graduate Students (top 1\%), 2023
  \item CUBA (Shandong) --- Third Place, 2022
  \item National Scholarship for Undergraduates (top 1\%), 2020
  \item Song Jian Scholarship (top 0.1\%), 2020
  \item Meritorious Winner, Mathematical Contest in Modeling (MCM/ICM), 2019
\end{itemize}

% -------------------------- Professional Service ---------------------
\section{Professional Service}
Reviewer: IEEE Robotics and Automation Letters (RA-L); International Journal of Robotics Research (IJRR).

\vfill
{\footnotesize\color{gray}Last updated: June 2026.}

\end{document}
